\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Fix sentence about unsupervised methods not needing data

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. When training data for a particular problem is scarce, it is logical that unsupervised methods will perform well, as they do not rely on training data. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.

>>>>

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. When training data for a particular problem is scarce, it is logical that unsupervised methods will perform well, as they require less data than supervised methods. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.
